---
title: "mmstat,data"
author: 
- name: "Sigbert Klinke" 
  email: sigbert@hu-berlin.de
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
vignette: > 
  %\VignetteIndexEntry{wwwdata} 
  %\VignetteEngine{knitr::rmarkdown} 
  \usepackage[utf8]{inputenc} 
---

```{r, echo = FALSE, message = FALSE}
library("wwwdata")
```

# General
 
`mmstat.data` is a package to load data sets either locally of fromb internet. 

# `wwwdata`

## Basic usage

You load a data set by

```{r}
library("mmstat.data")
data(dasl.titanic, verbose=TRUE)
str(dasl.titanic)
``` 

The package masks the `data` command from the package `utils`. However, when the data set name is not found in list
of available commands then `utils::data` will be called.

```{r}
data(Titanic)
str(Titanic)
``` 

An overview of available data set can be found via

```{r}
library("mmstat.data")
 # numbers of integrated data sets
length(getOption("wwwdata"))
# names of the first six data sets
head(names(getOption("wwwdata")))
# names and URLs of the first six data sets
head(getOption("wwwdata"))
``` 

## How does it work

During installation or the first call of `library("mmstat.data")` in the home directory a directory `.mmstat` is created. It downloads once the file [`https://github.com/sigbertklinke/wwwdata/raw/master/wwwdata/wwwdata.txt`](https://github.com/sigbertklinke/wwwdata/tree/master/wwwdata) which contains the location of the data project. For each project it downloads the `zzz.R` file which sets the data and URL names during loading. For an example see [`ansur2/zzz.r`](https://github.com/sigbertklinke/wwwdata/tree/master/wwwdata/ansur2).

Whenever a data set is loaded then it will stored in the local directory `.mmstat`, too. Subsequent calls will take the data from there.

# `concepts`

`concepts` extracts all keywords or concepts from the Rd files of a package.

```{r}
# concepts and keywords from wwwdata
concepts()
# concepts and keywords from stats
concepts('stats')
```
```{r, eval=FALSE}
# concepts and keywords from all installed packages (takes some time!)
concepts(NULL)
```

# `extract`

# Frequently asked questions

## Does the package require a permanent internet connection?

No, only the first time the package or one of the data sets is loaded. It uses the local directory `.mmstat` for storage to minimize the number of downloads. 

## Which data sets are currently included?
* `ansur2` (2): Anthropometric Survey of US Army Personnel from https://www.openlab.psu.edu/ansur2/
* `dasl` (519): The Data And Story Library from https://dasl.datadescription.com/ 